\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-12-13 write_up/cricket.tex
better graphs

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Type of Match}
\includegraphics[scale=.85]{../figs/winbyType.pdf}
\label{fig:type}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Type of Match.}
\begin{minipage}{0.85\textwidth}
\centering
\includegraphics[scale=.85]{../figs/winbyType.pdf}
{\footnotesize Note: \emph{n} refers to the number of matches.\par}
\end{minipage}
\label{fig:type}
\end{figure}
